---
title: "Homework 1"
author: Kate Dunn
output: github_document
---

**P8105 Homework 1**

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
```

# Problem 1

The purpose of this report is to describe the penguins dataset using both 
summary measures and plots. 

## Loading the penguins data set to enviornment

The following code calls the dataset which will be reported on, and lists its source R package. 

```{r}
data("penguins", package = "palmerpenguins")
```


## Description of the penguins dataset and variables


- The dataset "penguins" from the package "palmerpenguins" contains the variables: 

  **`r names(penguins)`**

- Species of penguins include: 

  **`r levels(penguins$species)`**

- Islands inhabited include:

  **`r levels(penguins$island)`**

- There are **`r nrow(penguins)`** rows and **`r ncol(penguins)`** columns in the dataset

- The mean flipper length is **`r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), 2)` mm**

## Penguin flipper and bill length

The following plot shows flipper length plotted against bill length (both in mm), and is grouped
by species, illustrated by point color. 

```{r,  echo = FALSE, message=FALSE, warning=FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
    geom_point() +
    labs(title = "Bill Length vs. Flipper Length",
       x = "Bill Length (mm)",
       y = "Flipper Length")
```

