---
title: "Homework 1"
author: Kate Dunn
output: github_document
---

**P8105 Homework 1**

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
```

# Problem 1

The purpose of this report is to describe the penguins dataset using both 
summary measures and plots. 

## Loading the penguins data set to enviornment

The following code calls the dataset which will be reported on, and lists its source R package. 

```{r}
data("penguins", package = "palmerpenguins")
```


## Description of the penguins dataset and variables


- The dataset "penguins" from the package "palmerpenguins" contains the variables: 

  **`r names(penguins)`**

- Species of penguins include: 

  **`r levels(penguins$species)`**

- Islands inhabited include:

  **`r levels(penguins$island)`**

- There are **`r nrow(penguins)`** rows and **`r ncol(penguins)`** columns in the dataset

- The mean flipper length is **`r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), 2)` mm**

## Penguin flipper and bill length

The following plot shows flipper length plotted against bill length (both in mm), and is grouped
by species, illustrated by point color. 

```{r,  echo = FALSE, message=FALSE, warning=FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
    geom_point() +
    labs(title = "Bill Length vs. Flipper Length",
       x = "Bill Length (mm)",
       y = "Flipper Length")
ggsave("Flipper_Bill_Plot.pdf")
```

# Problem 2

The purpose of this report is to generate a dataframe and investigate variable types.

## Creating dataframe
The following code generates a dataframe of size 10rows x 4columns of different variable types. 

```{r}
set.seed(27)

homework_1_df = tibble(
  hw1_sample = rnorm(10),
  hw1_over_zero = hw1_sample > 0,
  hw1_char = c( "a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  hw1_factor = factor(c("good", "bad", "ugly", "ugly", "good", "good", "ugly", "bad", "good", "bad"))
)
```
The resultant dataframe is as follows:

```{r,  echo = FALSE, message=FALSE, warning=FALSE}
homework_1_df

```